---
title: "nullrangesData package"
output:
  rmarkdown::html_document
vignette: |
  %\VignetteIndexEntry{nullrangesData package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The *nullrangesData* package provides datasets for the *nullranges*
package vignette, in particular example datasets for exclusion
regions, DNase hypersensitivity sites (DHS), CTCF binding sites,
and CTCF genomic interactions.

```{r}
library(nullrangesData)
suppressPackageStartupMessages(library(GenomicRanges))
suppressPackageStartupMessages(library(InteractionSet))
```

Excluded regions (see `?exclude` for details).

```{r}
data("exclude")
exclude
```

A549 DHS peaks (see `?DHSA549Hg38` for details).

```{r}
data("DHSA549Hg38")
DHSA549Hg38
```

CTCF binding sites, 10kb bins with CTCF and DHS peaks, and CTCF-bound
genomics interactions. See corresponding man pages for details.

```{r}
data("CTCF_hg19")
data("hg19_10kb_bins")
data("hg19_10kb_ctcfBoundBinPairs")
CTCF_hg19
hg19_10kb_bins
```

# Session information

```{r}
sessionInfo()
```
